---
title: "Simple document"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r, message = FALSE, echo = FALSE}
library(tidyverse)
```


Legend
YAML header: The segment at the beginning of the document bracketed by ---s.
Text + inline R: Written text with simple formatting like # heading, **bold**, and _italic_
Code chunks: Blocks of code surrounded by ```

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

Use option+command+i for codes {r}

```{r, results='hide'}
#This is a comment, but usually there is no need for this setup.
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r round(mean(samp),2)`.

Rounding function is round(mean(samp), decimal places)

# Section 3

<!-- to comment a text -->

this is going to make a plot

```{r, chunk_scatterplot}
plot_df = 
  tibble(
    x = rnorm(n = 1000),
    y = 1 + 2*x^2 + rnorm(n = 1000)
  )
plot_df

ggplot(plot_df, aes(x = x)) + geom_histogram()

gpp = ggplot(plot_df,aes(x = x, y = y)) + geom_point()

ggsave("scatter_plot.pdf", heigh = 4, width = 6)
```

# Section 4
Learning assessment: Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE

```{r}
example_df = #need to fill the entire dataframe -- 5:18 wouldn't work bc 10 empty rows
    tibble( #tibble is a function
      vec_numeric = rnorm(n = 500, mean = 1),
      vec_logical = vec_numeric > 0,
      vec_num2 = abs(vec_numeric),
    )
ggplot(example_df, aes(x = vec_num2)) + geom_histogram()
round(median(pull(example_df, vec_num2)), 2)
```

* list item 1
* list item 2

First header | second header
----------- | --------------
  content 1 | content 1
  content 2 | content 2

* list 1
  